---
title: "CPA Daily Monitoring Report(Adolescent)"
author: "MH Khan"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M ')`"
output:
  html_document:
    code_folding: hide
    toc: true
    theme: paper
---


```{r include=FALSE, warning = FALSE, message=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning = FALSE)

library(dplyr)
library(sf)
library(HighFrequencyChecks)
library(srvyr)
library(anytime)
library(readr)
library(stringr)
library(ggplot2)
library(lubridate)
library(rgdal)
library(HighFrequencyChecks)
library(kableExtra)
library(gsubfn)
library(stringi)
library(data.table)
library(sf)
# library(GISutils)
library(tmap)
library(butteR)
library(AMR)
source("Functions/GIS_Project_Functions.R")
source("Functions/Load_Audit.R")
source("Functions/get_na_response_rates.R")


#load data

camp_boundary_gdb<- "D:\\mh1\\REACH\\Common_shape_files\\190310_outline_rohingya_refugee_camp_a1"
camp_boundary<-st_read(dsn=camp_boundary_gdb,layer ="190310_Outline_Rohingya_Refugee_Camp_A1" )
data_path <- "D:\\mh1\\REACH\\cpp\\CPP\\04 Data\\01_adolescent\\01_data_collection/"
# dropbox_hh_path <- paste0(dropbox_path,"daily_data\\",str_replace_all(ymd(day_to_run),"-","_"),"_hh_Data.csv")
date_log_path <- "D:\\mh1\\REACH\\cpp\\CPP\\Output\\date_log/adolescent/date_logger.csv"
hh <- read.csv(paste0(data_path,"daily_data/","HH.csv"))
indv <- read.csv(paste0(data_path,"daily_data/","indv.csv"))
long_lat<-c("X_gps_reading_longitude","X_gps_reading_latitude")
target_points <- st_read("Output/sampling/kml/Adol/round1/merge_adol_finalV3.kml")
buffer <-25

############################date log##############################

hh$reported_date <- ymd(substr(hh$survey_start,1,10))
date_log_full<- hh %>% select(X_index,X_uuid,reported_date)

if(write_csv_output=="yes"){
date_log_track <- paste0("D:\\mh1\\REACH\\cpp\\CPP\\Output\\date_log/adolescent/",str_replace_all(day_to_run,"-","_"),"_date_logger.csv") 
write.csv(date_log_full,date_log_path,row.names=FALSE)
file.copy(from = date_log_path,to = date_log_track,overwrite = T)
}
```

```{r include=TRUE, warning = FALSE, message=FALSE}

hh_spatial <- st_as_sf(hh,coords = long_lat) %>% st_set_crs(4326)
hh_spatial_corrected <- hh_spatial %>% st_join(camp_boundary,st_intersects)  
hh_spatial_corrected_yes_consent <- hh_spatial_corrected %>% dplyr::filter(consent == "yes")
hh_spatial_corrected_yes_consent_df <- hh_spatial_corrected_yes_consent %>% as.data.frame() %>% select(-contains("gps")) %>%  select(-"geometry")

hh_spatial_corrected_desensitize <- hh_spatial_corrected %>% as.data.frame() %>% select(-"geometry")  %>% select(-contains("gps"))

hh_to_output_path <- "C:\\Users\\MEHEDI\\Dropbox\\REACH_BGD\\REACH\\Ongoing\\70DYL - UNICEF (Child Protection)\\04 Data\\01_adolescent/01_data_collection\\daily_data/"

if(write_csv_output == "yes"){
write.csv(hh_spatial_corrected_desensitize,paste0(hh_to_output_path,str_replace_all(day_to_run,"-","_"),"_HH.csv"))
write.csv(indv,paste0(hh_to_output_path,str_replace_all(day_to_run,"-","_"),"_INDV.csv"))
}
```

## Progress Tracking
Total number of survey so far is **`r nrow(hh)`**.
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
sample_size <- read.csv("Inputs/Sampling/adol/kmz_sample_request_CP adol survey_happening_all.csv") 
sample_size <- sample_size %>% dplyr::filter(sample_size$number_points_w_buffer != "" )

complete_by_camp<-hh_spatial_corrected %>% 
  group_by(New_Camp_N) %>% 
  summarise(
    num_complete=sum(consent =="yes"),
    num_consent_no=sum(consent =="no"),
    num_not_shelter = sum(consent =="shelter_not"),
    num_not_respondent = sum(consent =="respondent_not"),
    number_pts=n()) %>% 
  full_join(sample_size,by=c("New_Camp_N"= "New_Camp_N"), all.x=TRUE, all.y=TRUE) %>% 
  mutate(
    points_visited=ifelse(is.na(number_pts),0,number_pts),
    number_complete= ifelse(is.na(num_complete),0,num_complete),
    number_consent_no= ifelse(is.na(num_consent_no),0,num_consent_no),
    number_shelter_not= ifelse(is.na(num_not_shelter),0,num_not_shelter),
    number_respondent_not= ifelse(is.na(num_not_respondent),0,num_not_respondent),
    points_needed=points_needed,
    points_remaining=points_needed-number_complete,
  ) %>% 
select(New_Camp_N,points_needed, number_points_w_buffer,points_visited, number_complete ,points_remaining, number_consent_no,number_shelter_not,number_respondent_not)%>% 
  arrange(New_Camp_N) %>% as.data.frame() %>% select(-"geometry")

#total number of survey by date 
survey_by_date <- hh %>% dplyr::group_by(reported_date) %>% dplyr::summarise(
  number_of_survey = n()
)

survey_by_date %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Total number of survey by date ") %>% kable_styling(position = "center")

complete_by_camp %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Tracking sheet (NA means the points fall outside the camp boundary) ") %>% kable_styling(position = "center")
```

## GIS Checks
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
 
distance <- butteR::check_distances_from_target(dataset = hh_spatial_corrected ,target_points = target_points,dataset_coordinates = long_lat, cols_to_report = c("reported_date","New_Camp_N", "X_uuid","enumerator_id"), distance_threshold = buffer)

distance %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Surveys fall outside of 25m from the assigned GPS point ") %>% kable_styling(position = "center")


```


## Duration 
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}

path_unzip <- "Inputs\\adolescent\\98_temp"
audit_zip_dir<-"D:\\mh1\\REACH\\cpp\\CPP\\04 Data\\01_adolescent\\01_data_collection\\01_audit"
audit_zipfile <-paste0(audit_zip_dir,"/aFNiyg82tm8nVLwuQawJr6_",str_replace_all(day_to_run,"-","_"),".zip")
copy_zip_to<-paste0("D:\\mh1\\REACH\\cpp\\CPP\\Inputs\\adolescent\\01_audit/",day_to_run,".zip")
audit_node<-"/aFNiyg82tm8nVLwuQawJr6/"

audit_yes<-Load_Audit(data=hh, 
                      path.to.zip = audit_zipfile,
                      path.to.unzip = path_unzip,
                      copy.zip = TRUE,
                      path.to.copy.zip = copy_zip_to,
                      delete.unzipped=TRUE
)

#########last eituku porjnto dekhc

dfl<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"consent")& !is.na(event)) %>% 
    select(end) 
  start_question<-min(start_question$end)
  end_question<-d %>% filter(node==paste0(audit_node,"meta_data/end_interview")& !is.na(node)) %>% 
    select(start)
  end_question<-max(end_question$start)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl[[i]]<-data.frame(uuid=names(audit_yes)[i],duration_ms=duration_ms,durations_secs=duration_secs,duration_minutes= duration_minutes)
}

duration_df2<-do.call("rbind", dfl)

htdf<-hh_spatial_corrected_yes_consent %>%  
  left_join(duration_df2, by= c("X_uuid"="uuid")) %>% as.data.frame()

is.na(htdf$duration_minutes) <- sapply(htdf$duration_minutes,is.infinite) #inf or -inf to NA

```

### Duration Statistics
Statistics on survey duration are calculated from the audit file and are now correct.

The mean time for a completed questionaire so far is **`r mean(htdf$duration_minutes, na.rm=TRUE)`**.

The median time for a completed questionaire so far is **`r median(htdf$duration_minutes, na.rm=TRUE)`**.



```{r eval=TRUE, echo=FALSE, results='asis'}

# quick_surveys<-htdf[htdf$duration_minutes< mindur,]

mindur <- 30
quick_surveys<-htdf %>% filter(duration_minutes < mindur)

quick_survey_daily<-quick_surveys %>% group_by(reported_date, enumerator_id) %>% 
  select(reported_date, enumerator_id, X_uuid,duration_minutes, New_Camp_N) %>% arrange(reported_date)

quick_survey_information<-data.frame(quick_surveys$enumerator_id,quick_surveys$X_uuid, quick_surveys$duration_minutes)

duration_by_enumerator <- htdf %>%
  mutate(zscore = scale(duration_minutes),
  zscoreLog = scale(log(duration_minutes))) %>%
  group_by(enumerator_id) %>%
  summarise(
  number_surveys=n(),  
  mean_duration = mean(duration_minutes, na.rm = TRUE),
  median_duration = median(duration_minutes, na.rm=TRUE)
  ) %>%
  ungroup %>%
  mutate(
  difference_from_mean = mean_duration - mean(htdf$duration_minutes,na.rm=TRUE),
  difference_from_median = median_duration - median(htdf$duration_minutes,na.rm=TRUE)
  )


quick_survey_daily%>% kable( longtable = T, booktabs = T, linesep = "",caption= paste0("Enumerators That Completed a Full Survey In Less Than ",mindur, " minutes")) %>% kable_styling(position = "center")

duration_by_enumerator%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Duration Statistics By Enumerator (minutes)") %>% kable_styling(position = "center")

```

### Consent
```{r eval=TRUE, echo=FALSE, results='asis'}
#Identify any surveys in which time spent on consent is less than 45 seconds 
dfl1<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"consent_message")& !is.na(event)) %>% 
    select(start) 
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"consent_message")& !is.na(node)) %>% 
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl1[[i]]<-data.frame(uuid=names(audit_yes)[i],consent_duration_ms=duration_ms,
                        consent_durations_secs=duration_secs,
                        consent_duration_minutes= duration_minutes)
}

duration_df3<-do.call("rbind", dfl1)

htdf1<-hh_spatial_corrected_yes_consent %>%  
  left_join(duration_df3, by= c("X_uuid"="uuid")) %>% as.data.frame()

is.na(htdf1$consent_duration_minutes) <- sapply(htdf1$consent_duration_minutes,is.infinite)

# quick_surveys<-htdf[htdf$duration_minutes< mindur,]

mindur1 <- 45
quick_surveys<-htdf1 %>% filter(consent_durations_secs < mindur1)


quick_survey_daily<-quick_surveys %>% group_by(reported_date, enumerator_id) %>% 
  select(reported_date, enumerator_id, X_uuid,consent_durations_secs, New_Camp_N) %>% arrange(reported_date)


quick_survey_daily%>% kable( longtable = T, booktabs = T, linesep = "",caption= paste0("Enumerators who spent Less Than ",mindur1, " seconds on consent")) %>% kable_styling(position = "center")

```

### HarmThreats
```{r eval=TRUE, echo=FALSE, results='asis'}
#Identify any surveys in which time spent on consent is less than 45 seconds 
dfl4<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"meta_data/harmthreats/witness_threats")& !is.na(event)) %>% 
    select(start) 
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"meta_data/harmthreats/witness_threats")& !is.na(node)) %>% 
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl4[[i]]<-data.frame(uuid=names(audit_yes)[i],harmthreats_duration_ms=duration_ms,
                        harmthreats_durations_secs=duration_secs,
                        harmthreats_duration_minutes= duration_minutes)
}

duration_df4<-do.call("rbind", dfl4)

htdf4<-hh_spatial_corrected_yes_consent %>%  
  left_join(duration_df4, by= c("X_uuid"="uuid")) %>% as.data.frame()

is.na(htdf4$harmthreats_durations_secs) <- sapply(htdf4$harmthreats_durations_secs,is.infinite)

# quick_surveys<-htdf[htdf$duration_minutes< mindur,]

mindur4 <- 45
quick_harmthreat<-htdf4 %>% filter(harmthreats_durations_secs < mindur4)

quick_harmthreat_survey<-quick_harmthreat %>% group_by(reported_date, enumerator_id) %>% 
  select(reported_date, enumerator_id, X_uuid,harmthreats_durations_secs, New_Camp_N) %>% arrange(reported_date)

quick_harmthreat_survey %>% kable( longtable = T, booktabs = T, linesep = "",caption= paste0("Enumerators who spent less than ",mindur4, " seconds on threats question")) %>% kable_styling(position = "center")

```

### servicehelp
```{r eval=TRUE, echo=FALSE, results='asis'}
#Identify any surveys in which time spent on consent is less than 45 seconds 
dfl5<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"meta_data/serviceshelp/rank_unmet_needs")& !is.na(event)) %>% 
    select(start) 
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"meta_data/serviceshelp/rank_unmet_needs")& !is.na(node)) %>% 
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl5[[i]]<-data.frame(uuid=names(audit_yes)[i],srvchlp_duration_ms=duration_ms,
                        srvchlp_durations_secs=duration_secs,
                        srvchlp_duration_minutes= duration_minutes)
}

duration_df5<-do.call("rbind", dfl5)

htdf5<-hh_spatial_corrected_yes_consent %>%  
  left_join(duration_df5, by= c("X_uuid"="uuid")) %>% as.data.frame()

is.na(htdf5$srvchlp_durations_secs) <- sapply(htdf5$srvchlp_durations_secs,is.infinite)



mindur5 <- 25
quick_srvchlp<-htdf5 %>% filter(srvchlp_durations_secs < mindur5)


quick_srvchlp_survey<-quick_srvchlp %>% group_by(reported_date, enumerator_id) %>% 
  select(reported_date, enumerator_id, X_uuid,srvchlp_durations_secs, New_Camp_N) %>% arrange(reported_date)


quick_srvchlp_survey %>% kable( longtable = T, booktabs = T, linesep = "",caption= paste0("Enumerators who spent less than ",mindur5, " seconds on unmet needs question ")) %>% kable_styling(position = "center")

```

### Daily Act
```{r eval=TRUE, echo=FALSE, results='asis'}
paid_per_day <- hh_spatial_corrected_yes_consent_df %>% dplyr::filter(resp_work_pay > 500) %>% select(reported_date, enumerator_id, X_uuid, New_Camp_N,resp_work_pay)

 irregular_at_learning_center <- hh_spatial_corrected_yes_consent_df %>% dplyr::filter( resp_activities_7 == "yes" & access_lc == "no") %>% select(reported_date, enumerator_id, X_uuid, New_Camp_N)
 
paid_per_day %>% kable( longtable = T, booktabs = T, linesep = "",caption="Surveys in which amount earned is more than 500 takas") %>% kable_styling(position = "center")

irregular_at_learning_center %>% kable( longtable = T, booktabs = T, linesep = "",caption="Surveys in which respondent says they attend a learning center for daily activities question but no to if they have attended a learning center in past 30 days") %>% kable_styling(position = "center")

```

## Enumerator
```{r warning = FALSE, message=FALSE}
#total col 37+22 =59
col_name_enu_si <- c("close_hc", "access_hc", "permission_hc", "yesno_challenges_hc", 
"access_lc", "permission_lc", "yesno_challenges_lc", "access_cp", 
"permission_cp", "yesno_challenges_cp", "camp_safe", "work_chores", 
"work_shelter", "work_phys_chores", "work_sibs", "work_outside", 
"work_dang", "work_constr", "work_stop_school", "marr_par", "marr_dowry", 
"marr_burden", "marr_safe", "marr_drop_school_girl", "marr_drop_school_boy", 
"marr_old_man", "marr_mom", "vio_fath", "vio_moth", "vio_discipline", 
"vio_husb", "vio_wife", "vio_teach", "vio_solve_prob", "negl_misbehave", 
"negl_stress", "negl_needs")
 
 
col_name_enu_multiple <- c("seek_treat.dontknow_prefer_not_answer", "not_seek_treat.dont_know", 
"who_permission_hc.dont_know", "if_challenges_hc.dont_know", 
"attend_a_learning_center.dont_know", "who_permission_lc.dont_know", 
"challenges_lc.dont_know", "child_protection_services.dont_know", 
"who_permission_cp.dont_know", "challenges_cp.dont_want_to_answer", 
"ask_help.dont_know", "ask_stress.dont_know", "ask_unsafe.dont_know", 
"ask_unsafe_outside.dont_know", "ask_physical_assistance.dont_know", 
"threats_30.dont_know", "report_child_work.dont_know", "report_child_vio_home.dont_know", 
"report_child_vio_teach.dont_know", "report_child_vio_sex.dont_know", 
"work_decide.dont_know", "marr_decide.dont_know")

hh_spatial_corrected_yes_consent_df <- hh_spatial_corrected_yes_consent_df %>% mutate(
  dontknow_prefer_not_to_ans_si = rowSums(hh_spatial_corrected_yes_consent_df[col_name_enu_si] =="dont_know",na.rm = T),
dontknow_prefer_not_to_ans_multiple = rowSums(hh_spatial_corrected_yes_consent_df[col_name_enu_multiple] =="1",na.rm = T),
rowsum_dont_know_enu = ( dontknow_prefer_not_to_ans_multiple + dontknow_prefer_not_to_ans_si))

enu_records_dont_know <- hh_spatial_corrected_yes_consent_df %>% dplyr::filter(rowsum_dont_know_enu > 30) %>% select(reported_date, enumerator_id, X_uuid, New_Camp_N,rowsum_dont_know_enu)


enu_records_dont_know %>% kable( longtable = T, booktabs = T, linesep = "",caption="Surveys that enumerators record “don’t know/prefer not to answer” for over half of the questions") %>% kable_styling(position = "center")
```

## General Checks
### Missing/ Duplicated GPS
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}

if(which(duplicated(hh$X_uuid)) %>% length()>0){ 
  cat("there ARE duplicated uuids in hh dataset")} else{cat ("there are NO duplicated uuids in hh data set")} 
```

### Start and end day is not same 
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
start_end_date <- hh_spatial_corrected_yes_consent %>% as.data.frame() %>%  select(survey_start,end_survey,reported_date,X_uuid,enumerator_id) %>% mutate(
  start_date = substr(hh_spatial_corrected_yes_consent$survey_start,1,10),
  end_date = substr(hh_spatial_corrected_yes_consent$end_survey,1,10),
  same_date = if_else(start_date == end_date,"yes","no")
)

not_same_date <- start_end_date %>% dplyr::filter(same_date == "no") %>% select(reported_date,enumerator_id,X_uuid,start_date,end_date) %>% dplyr::arrange(reported_date) 


not_same_date %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Surveys that do not end on the same day they started") %>% kable_styling(position = "center")

```

### Check NAs
NA response rates written to shared dropbox folder
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}

dropbox_aux<-"C:\\Users\\MEHEDI\\Dropbox\\REACH_BGD\\REACH\\Ongoing\\70DYL - UNICEF (Child Protection)\\04 Data\\01_adolescent\\01_data_collection/aux_outputs/"
dropbox_aux_na_path<-paste0(dropbox_aux,"NAresponses\\", str_replace_all(ymd(day_to_run),"-","_"))

hh_na<-get_na_response_rates(hh)


if(write_csv_output == "yes"){
write.csv( hh_na,paste0(dropbox_aux_na_path, "_NA_response_hh.csv"))
}

```

### Agree/disagree
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
col_names <- c("work_chores", "work_shelter", "work_phys_chores", "work_sibs", 
"work_outside", "work_dang", "work_constr", "work_stop_school", 
"marr_par", "marr_dowry", "marr_burden", "marr_safe", "marr_drop_school_girl", 
"marr_drop_school_boy", "marr_old_man", "marr_mom", "vio_fath", 
"vio_moth", "vio_discipline", "vio_husb", "vio_wife", "vio_teach", 
"vio_solve_prob", "negl_misbehave", "negl_stress", "negl_needs"
)

hh_spatial_corrected_yes_consent_df <- hh_spatial_corrected_yes_consent %>% as.data.frame()

hh_spatial_corrected_yes_consent_df$rowsum_agree <- rowSums(hh_spatial_corrected_yes_consent_df[col_names] == "agree",na.rm = T)

hh_spatial_corrected_yes_consent_df$rowsum_dis_agree <- rowSums(hh_spatial_corrected_yes_consent_df[col_names] == "disagree",na.rm = T)

hh_spatial_corrected_yes_consent_df$rowsum_dont_know <- rowSums(hh_spatial_corrected_yes_consent_df[col_names] == "dont_know",na.rm = T)

ag_disag_dnkn <- hh_spatial_corrected_yes_consent_df %>% dplyr::filter(rowsum_agree >24 | rowsum_dis_agree > 24 |rowsum_dont_know >24 | rowsum_agree == rowsum_dis_agree) %>% select(reported_date,X_uuid,enumerator_id,rowsum_agree,rowsum_dis_agree,rowsum_dont_know)

ag_disag_dnkn %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Enumerators who have a clear pattern of responses to the agree/disagree questions across their surveys") %>% kable_styling(position = "center")

```

### Other response
Other responses are written to shared dropbox folder
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}

  hh_other<-hh%>% 
    filter_at(vars(ends_with("_other")), any_vars(!is.na(.))) %>% 
    select(X_uuid,enumerator_id,reported_date, ends_with("_other"))
if(write_csv_output == "yes"){
write.csv(hh_other,paste0(dropbox_aux,"Otherresponse/",str_replace_all(day_to_run,"-","_"),"_Other.csv"))
}
```
